### 2019-10-03 vesicle_code/docs/softmatter/permeableVes.tex
soft matter TeX
starting literature review for semiperemable

@@

Following the analysis of~\cite{vee-gue-zor-bir2009} and
disregarding background flow, we define scales of $\mbx$, $t$, $\beta$,
and $c$ to nondimensionalize equation (\ref{eq:full}) as follows. The
length is scaled using the radius of a circle with the same perimeter,
$L$, as the vesicle, $R_0 = \frac{L}{2\pi}$. From analysis, the time
scale $\tau$ is defined as $\tau = \frac{\mu R_0^2}{k_b}$, the tension
scale, $Q$, is defined as $Q = \frac{k_b}{R_0^2}$, the water flux scale,
$W$, is defined as $W=\frac{R_0}{\mu}$, and the concentration scale,
$C$, is defined as $C=\frac{k_b}{R_0^3RT}$. The governing equation in
nondimensional form is
\begin{align}
    \dot{\Tilde{\mbx}} = \Tilde{\mbu}_{\infty} + \Tilde{\beta}\jump{\tilde{c}}\mbn +
    \Tilde{\beta}P\big(B[\Tilde{\mbx}]\Tilde{\mbx}+T[\Tilde{\mbx}]\Tilde{\sigma}\big)
    +\sgl\big( B[\Tilde{\mbx}]\Tilde{\mbx} + T[\Tilde{\mbx}]\Tilde{\sigma}\big).
\end{align}
In our current implementation, we let $\jump{c} = 0$. The remaining equations are written in dimensionless form, unless stated otherwise, and for simplicity of notation we remove the tildes.

>>>>

\begin{itemize}
  \item Yao and Mori~\cite{yao-mor2017} use an immersed boundary method
    to simulate osmotic water flow and solute diffusion with a
    deformable elastic membrane.

  \item Anderson~\cite{and1983} seems to be the first to consider
    semipermeable vesicles with an osmotic gradient. This work describes
    the governing equations and does a non-dimensionalization. The
    scaling behavior of the vesicle velocity with respect to the
    concentration Peclet number is analyzed.

  \item Gupta et al.~\cite{gup-sre-tha2015} consider diffusio-phoretic
    motion of a deformable vesicle. The vesicle has a certain region
    that is chemically active while the rest of the vesicle is
    noncatalytic. A L-J model is used to describe the molecular motion
    in the catalytic region and this generates self-propulsion.

  \item Jayathilake et al.~\cite{jay-kho-tan2010} consider a permeable
    capsule being adhered to a substrate. They use an immersed interface
    method developed by Leveque and Li in 1994.

  \item Jayathilake et al.~\cite{jay-tan-kho-wij2010} consider osmotic
    swelling of a deformable elastic membrane. Again, they use an
    immersed interface method. The formulation and methods are very
    close to the work of Anita Layton~\cite{lay2006}.

  \item In Jayathlake's Ph.D.~thesis~\cite{jay2010}, he states that a
    BIE could be used, but it is not applicable for non-linear problems.
    This is not an issue for us since we are interested in the linear
    Stokes equations. Section 2.2.1 gives the model formulation
    including the non-dimensionalization.

  \item Layton~\cite{lay2006} simulates water transport across a
    elastic water-permeable membrane. Instead of an immersed boundary
    method, she uses a finite difference method and incorporates the
    interface using the modified stencils developed my Anita
    Mayo~\cite{may1984}.  The numerical methods are fairly standard.

  \item Li, Mori, and Sun~\cite{li-mor-sun2015} study flow-driven cell
    migration in electric fields.  The cell boundaries include water and
    ionic fluxes.

  \item Liu et al.~\cite{liu-chu-new-rea-low-all2019} consider the
    physical contact between pairs of permeable membranes. This might be
    useful when we consider suspensions of semi-permeable vesicles.
    Model parameters, including the membrane permeability, are given in
    Table 1. They use a stochastic immersed boundary method.

  \item Nardi et al.~\cite{nar-bru-sac1999} describe how vesicles in a
    concentration gradient are osmotic motors. This is an experimental
    paper that shows a velocity that is much larger than what the theory
    predicts.

  \item Stockie~\cite{sto2009} considers flow through porous immersed
    boundaries. The method uses an immersed boundary method and the flow
    through the membrane flux is described with Darcy's law.

\end{itemize}

@@

Following the analysis of~\cite{vee-gue-zor-bir2009} and
disregarding background flow, we define scales of $\mbx$, $t$, $\beta$,
and $c$ to nondimensionalize equation (\ref{eq:full}) as follows. The length is scaled using the radius of a circle with the same perimeter,
$L$, as the vesicle, $R_0 = \frac{L}{2\pi}$. The shear rate, $\chi$, is scaled by $\frac{\mu R_0^3}{\kappa_b}$ [REF] and $\Tilde{\mbu}_{\infty} = \Tilde{\chi}(\mbx_2,0)$. From analysis, the time
scale $\tau$ is defined as $\tau = \frac{\mu R_0^2}{k_b}$, the tension
scale, $Q$, is defined as $Q = \frac{k_b}{R_0^2}$, the water flux scale,
$W$, is defined as $W=\frac{R_0}{\mu}$, and the concentration scale,
$C$, is defined as $C=\frac{k_b}{R_0^3RT}$. The governing equation in
nondimensional form is
\begin{align}
    \dot{\Tilde{\mbx}} = \Tilde{\mbu}_{\infty} + \Tilde{\beta}\jump{\tilde{c}}\mbn +
    \Tilde{\beta}P\big(B[\Tilde{\mbx}]\Tilde{\mbx}+T[\Tilde{\mbx}]\Tilde{\sigma}\big)
    +\sgl\big( B[\Tilde{\mbx}]\Tilde{\mbx} + T[\Tilde{\mbx}]\Tilde{\sigma}\big).
\end{align}
In our current implementation, we let $\jump{c} = 0$. The remaining equations are written in dimensionless form, unless stated otherwise, and for simplicity of notation we remove the tildes.
